%-------------------------
% Yash Agarwal - Master one-page resume
% ATS-friendly. Edit this file; the permanent link recompiles automatically.
%------------------------

\documentclass[letterpaper,10pt]{article} % Set to 10pt for more space

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tight margins for maximum content density
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.9in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - tight spacing
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Yash Agarwal} \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8140724216 $|$ \href{mailto:2004agarwalyash@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{2004agarwalyash@gmail.com}} $|$
    \href{https://linkedin.com/in/XploY04}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/XploY04}} $|$
    \href{https://github.com/XploY04}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/XploY04}} $|$
    \href{https://linktr.ee/XploY04}{\raisebox{-0.2\height}\faGlobe\ \underline{linktr.ee/XploY04}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Bengaluru, India}
      {B.E. in Information Science and Engineering; CGPA: 8.9}{Sep. 2023 -- June 2027}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, TypeScript, SQL} \\
     \textbf{Backend \& Infra}{: FastAPI, Node.js, REST, WebSockets, Docker, Kubernetes (CRDs), GCP (Cloud Run), AWS (S3), Redis, Dramatiq, SQS, CI/CD} \\
     \textbf{Data \& AI}{: PostgreSQL (tsvector/GIN full-text search), MongoDB, Supabase, Pinecone (RAG), Gemini \& OpenAI Structured Outputs, Prometheus, Grafana, Datadog}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Mar. 2026 -- Present}
      {\href{https://remotestar.io/}{RemoteStar}}{Remote}
      \resumeItemListStart
        \resumeItem{Built on-demand, per-job resume analysis in Go that scores candidate-job fit through OpenAI Structured Outputs, backed by Redis per-user and per-job locks, a 7-day result cache, and a credit ledger that charges on request and refunds on failure.}
        \resumeItem{Moved resume parsing to a strict Structured Outputs schema, rebuilt the tailoring pipeline for one-page output from Tika text plus parsed JSON, and added an SQS queue with Gotenberg for HTML-to-PDF rendering.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Apr. 2026 -- Present}
      {\href{https://www.finalroundai.com/}{Final Round AI}}{Remote}
      \resumeItemListStart
        \resumeItem{Built the Report V2 interview-report backend (Python, Node) with per-question and aggregate scoring stages and an evidence gate that blocks any report from completing without backing evidence, plus GCS input recovery and Datadog lifecycle metrics.}
        \resumeItem{Fixed blank report emails affecting ~40\% of recent reports by publishing the RabbitMQ end event on session timeout, and replaced a blocking \texttt{requests.delete} in an async payment path with \texttt{httpx.AsyncClient}.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer Intern}{July 2025 -- Feb. 2026}
      {\href{https://seeqlo.com/}{Seeqlo}}{Remote}
      \resumeItemListStart
        \resumeItem{Wrote the backend in Go as a REST API for student-teacher workflows, and set up staging and production environments (Docker Compose on GCP Cloud Run, Firebase Hosting) that removed manual deployment.}
        \resumeItem{Enforced student, teacher, and admin RBAC with Firebase Security Rules across collections, and built the backend for an AI presentation generator on the Gemini API with real-time sync and auto-save.}
      \resumeItemListEnd

    \resumeSubheading
      {LFX Mentee, CloudNativePG}{Sep. 2025 -- Dec. 2025}
      {\href{https://github.com/cloudnative-pg/chaos-testing}{Cloud Native Computing Foundation (CNCF)}}{Remote}
      \resumeItemListStart
        \resumeItem{Built a chaos-testing harness that deletes the PostgreSQL primary in a 3-instance CloudNativePG cluster under load and verifies recovery with Jepsen consistency checks and Prometheus probes, confirming sub-minute failover with no data loss.}
        \resumeItem{Automated the full flow in GitHub Actions: provision a Kind cluster, install the CloudNativePG operator and LitmusChaos, inject primary pod deletion, run Jepsen, and export result artifacts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------OPEN SOURCE CONTRIBUTIONS-----------
\section{Open Source Contributions}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Kubeflow (CNCF) -- Contributor}{Go, Python, Kubernetes CRDs}
      {Distributed training and TrainJob lifecycle}{}
      \resumeItemListStart
        \resumeItem{Contributed a Megatron-Core GPT tensor-parallelism example to Kubeflow Trainer (\href{https://github.com/kubeflow/trainer/pull/3201}{PR \#3201}) that runs multi-GPU distributed training on a TrainJob, and authored the matching Trainer user guide.}
        \resumeItem{Authored and implemented the TrainJob lifecycle proposal adding \texttt{activeDeadlineSeconds} and \texttt{TTLSecondsAfterFinished} to the CRD (\href{https://github.com/kubeflow/trainer/pull/3068}{KEP \#3068}, \href{https://github.com/kubeflow/trainer/pull/3258}{impl \#3258}), and fixed all failing Kubeflow SDK E2E tests by handling Kubernetes 404/403 errors (\href{https://github.com/kubeflow/sdk/pull/307}{\#307}).}
      \resumeItemListEnd

    \resumeSubheading
      {LitmusChaos (CNCF Sandbox) -- Contributor}{Go, Kubernetes CRDs}
      {Precise pod targeting for operator-managed workloads}{}
      \resumeItemListStart
        \resumeItem{Shipped upstream \href{https://github.com/litmuschaos/chaos-operator/pull/510}{chaos-operator PR \#510} adding a \texttt{labelMatchMode} field and authored \href{https://github.com/litmuschaos/litmus-go/pull/777}{litmus-go PR \#777}, letting LitmusChaos target operator-managed pods such as a CloudNativePG primary by label intersection.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{\href{https://www.reelpin.in/}{ReelPin}} $|$ \emph{Python, FastAPI, Gemini, Pinecone, Supabase, Redis}}{\href{https://github.com/XploY04/reelpin-api}{GitHub}}
          \resumeItemListStart
            \resumeItem{Built the FastAPI backend and Dramatiq/Redis job queue that ingests Instagram Reels with yt-dlp, transcribes and categorizes them into a 46-category matrix with Gemini, and geocodes places via Google Maps into Supabase Postgres; 850+ reels, 50 users.}
            \resumeItem{Added natural-language search over saved reels by embedding transcripts into Pinecone for retrieval, and hardened the service with worker concurrency limits, retries with dead-lettering, rate limiting, and latency and error-rate alerting.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Reliance Foundation Scholarship} (top 5,000 of 100,000+ applicants nationwide); \textbf{Linux Foundation LiFT Scholarship}, 2026; \textbf{4th of 500 teams} at the Incubate Hackathon (JIPMER and IIT Bombay).}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
